A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-06-04 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

\documentclass[utf8]{article}

%% Language and font encoding
\usepackage[english]{babel}
%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
%\usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}

%% Title style
\usepackage{stringstrings}
\usepackage[explicit]{titlesec}
\usepackage{sectsty}

%% ============================== Useful packages ============================= %
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{svg}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}

%% ================================== acronym ================================= %
\usepackage{acronym}
\newacro{ntic}{non-trivial informational closure}
\newacro{ic}{informational closure}
\newacro{cg}{coarse-grain}
\newacro{cging}{coarse-graining}
\newacro{cged}{coarse-grained}
\newacro{ncg}{neural coarse-graining}

% The name of our theory
% ----------------------------------------------------------------------------
\newcommand{\tnamefull}{The Neural Coarse-graining Theory of Consciousness}
\newcommand{\tname}{NCGT} 	% TheoryNameShort
\newacro{\tname}{\tnamefull}
%\newacro{NCGT}{the neural coarse-graining theory of consciousness}

% =================================== Macro ================================== %
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[at]{easylist}
\usepackage{tcolorbox}
\tcbuselibrary{skins}
\usepackage{comment}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\usepackage{soul}
\usepackage{version}

% Meaning of colours --------------------------------------------------------- %
%	Red: Important and Critical
%	Orange: Todo
%	Blue: Topic and Guideline
%	Purple: Murmur
%	Green: Question, Call for help, Open for opinions and comments
%	Brown: Need Wording
% ---------------------------------------------------------------------------- %

% Real content
	% Outline items that can be integrated into main text
		\newenvironment{ants}
			{
			 \begin{easylist}[itemize]
		 	}
			{
			\end{easylist}
			} %

	% Writing Materials
    \newenvironment{WritingMaterials} %
    	{
            \begin{tcolorbox}[enhanced,
                title=-,
                size=small,
                colbacktitle=Aquamarine,
                drop fuzzy shadow,
                fontupper=\small,
                boxrule=0.4pt,
                colback=Aquamarine!10!white,
                sharp corners]
                Writing Materials
            \end{tcolorbox}
            \begin{easylist}[itemize]
    	}
    	{
            \end{easylist}  
            \begin{tcolorbox}[enhanced,
                halign=flush right,
                halign title=right,
                size=small,
                colbacktitle=Aquamarine,
                drop fuzzy shadow,
                fontupper=\small,
                boxrule=0.4pt,
                colback=Aquamarine,
                colupper=White,
                sharp corners]
                Writing Materials -
            \end{tcolorbox}        
    	}

    % \excludeversion{WritingMaterials}

% Functional content
	% Quotes: green
		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}

	% todo: orange
		% text todo
		\newcommand{\toWrite}[1]{\noindent
			\textcolor{Orange}{\textbf{[[ #1 ]]}}}

	% figure todo
        \newcommand{\includegraphicsTodo}[2][]{%
            \tcbox[enhanced,
                center,
            	adjusted title=\large To Be Modified ...,
            	halign title=center,
            	attach boxed title to top left={yshift=-3mm, xshift=1cm,yshifttext=-1mm}, boxed title style={drop fuzzy shadow},
            	colbacktitle=RedOrange!70!black,
            	coltitle=white,
            	colframe=RedOrange!50!black,
            	colback=white
        	]{\includegraphics[#1]{#2}}}

		% figure todo callout
        \newcommand{\needfig}[1]{%
			\ifthenelse{\equal{#1}{}}{%
				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig}}}{%
				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig: #1}}%
			}%
		}

		% rewording
		\newcommand{\rewording}[1]{\textcolor{RawSienna}{[[ REWORDING | #1 ]]}}

		% Need reference
		\newcommand{\needref}[1]{%
			\ifthenelse{\equal{#1}{}}{%
				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref}}}{%
				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref: #1}}%
			}%
		}

	% Highlight: Yellow or Red
		% Highlight only
		\newcommand{\highlight}[2][Yellow]{\sethlcolor{#1}\hl{#2}}

		% Highlight and comment
        \newcommand{\highlightAndComment}[3][Yellow]{\sethlcolor{#1}\hl{#2}\todo[color=#1, linecolor=Yellow]{#3}}

		% Critical point
		\newcommand{\critical}[1]{%
			\todo[color=OrangeRed!80!white]{#1}
		}

	% idea: Purple
		% text idea
			\newcommand{\idea}[2][Plum]{\noindent
				\textcolor{#1}{[[ #2 ]]}}

		% box idea
			\newcommand{\ideaBox}[1]{
			    \vspace{2mm}
				\begin{tcolorbox}[enhanced,%
                    title=-,
                    center,
                    fontupper=\small,
                    lifted shadow={1mm}{-2mm}{3mm}{0.1mm}{black!50!white},%
                    boxrule=0.4pt,
                    width=9cm,
                    colback=Thistle!50!white,
                    sharp corners]
					#1
				\end{tcolorbox}
				\vspace{2mm}
			}

		% call-out idea
			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}

	% communication: green
		% call for help
			\newcommand{\needhelp}[1]{\todo[color=SpringGreen]{[Need Help]: #1}}

		% comment
			% comment by authors
			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}

			% usage:
			% \addcomment{auther}{comment text}
			% or
			% \addcomment[highlighted text]{auther}{comment text}
			%
			% e.g.
			% It's a \addcomment[beautiful]{Acer}{need a reference} day

    % backup: 
    \newenvironment{backup}
    {

        \begin{tcolorbox}[enhanced,
            title=-,
            size=small,
            colbacktitle=black!70!white,
            colback=black!10!white,            
            drop fuzzy shadow,
            fontupper=\small,
            boxrule=0.4pt,
            sharp corners]
            Backup
        \end{tcolorbox}
    }
    {
        \begin{tcolorbox}[enhanced,
            halign=flush right,
            halign title=right,
            size=small,
            colbacktitle=black!10!white,
            colback=black!70!white,
            drop fuzzy shadow,
            fontupper=\small,
            boxrule=0.4pt,
            colupper=White,
            sharp corners]
            Backup -
        \end{tcolorbox}    
    }
    % \excludeversion{backup}

% review loop annotation
    \usepackage[xcolor, outerbars]{changebar}
    \cbcolor{red}

    % start anchor: \rlstart
    \newcommand{\rlstart}[1]{  %
        \setlength\changebarwidth{#1pt*2}  %
        \hspace*{-40pt}
        \cbstart{\textcolor{red}{\newline\textbf{iteration #1}}\newline}}

    % end anchor: \rlend
    \newcommand{\rlend}{\cbend}

% quote
\newcommand{\myQuote}[1]{\textit{``#1''}}

@@

    \newpage
    \section*{Not decided terminology}
        \begin{ants}
            @ information * in the NTIC process
            @ Full and short name of this theory
            @ core "?" (entity) for conscious content 
            @ our theory? framework? proposal? 
            @ system? process?
            @ variable? node? element? member?
        \end{ants}

@@

		% TODO: is figure needed?
		\idea{Do I need a figure?, Something like this one?}
		\begin{figure}[H]
			\includegraphicsTodo[width=\textwidth/2]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
			\cite{pennartz2017consciousness}
			\caption{xxxx}
	   	\end{figure}

@@

				\begin{figure}
					\includegraphics[width=\textwidth]{WritingMaterials/SystemAndEnv.pdf}
					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
					\label{fig:SystemAndEnv}
				\end{figure}

@@

			\begin{figure}[H]
				\includegraphicsTodo[width=\textwidth]{WritingMaterials/Palmer2015.png}
				\caption{Figure adapted from \cite{sederberg2018learning}}
				\label{fig:sederberg2018learning}
			\end{figure}

@@

		\begin{figure}
			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
			\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
			\label{fig:NCG}
		\end{figure}

@@

					@@ \rewrite{
						Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli. These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}

@@

	\section{A neural coarse graining theory of consciousness}

@@

				\begin{figure}[H]				
				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
				\label{fig:LevelOfConsciousness}
				\caption{Level of coarse-graining and level of consciousness. The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
				\end{figure}
		\end{ants}

@@

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
				\label{fig:hierarchy}
			\end{figure}

@@

	\section{Conscious versus Unconscious Processing}
		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
	    \ideaBox{I need to expend this section much more and more references}
	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
		Our theory indicates that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.

@@

		Take the neural system as an example, our theory can well explain previous empirical findings in consciousness science and further make strong and more precise predictions for future studies. In the following, we discussed the implication of the two necessary conditions with respect to the empirical data in the literature of consciousness.

		\subsection{Unconscious Processing}

        \subsubsection{Fail to meet 1\lowercase{st} condition}
\rlstart{4}        	
            As described above, if a process fails to fulfil either of the two conditions, information remains unconscious. First, We consider that a process fails to satisfy the first condition, i.e. the process fails to achieve NTIC. Many processes in the neural system fall into this category.

        	Considering the objectives of achieving NTIC (Equation \ref{eq:nticObjective}), if a process fails to maximise $I(Y_{t+1};Y_{t})$ or minimise $I(Y_{t+1};Y_{t}|E_{t})$, this results in low NTIC. The failure to maximise $I(Y_{t+1};Y_{t})$ implies the past states has small influence on its future states. In the meantime, if the process still receives environmental information and produces outputs, the future state of the process is largely determined by the past environmental states (fig.\ref{Fig:reflexive}), i.e. the process is not informational closed (${J_{t}(E \rightarrow Y )} \not\approx 0$).

@@

            In the context of information processing in the neural system, regarding to perception, this indicates that the perceptual processes only passively responds to the sensory inputs. Regarding to action, this indicates that the process only produces reflective-like behaviour. Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}. We hypothesise that this is a natural consequence when a process fails to meet the first condition.

            The same notion can be applied to blindsight and procedure memory \needref{blindsight}.
            Blindsight patients are able to track objects, avoid obstacles,and make above chance level judgements without conscious awareness of visual targets within the visual field without having any visual conscious experience. The direct stimulus-response mapping ($S\rightarrow{}R$) makes the internal neural circuit a non-NTIC process and results in unconscious processing. In the case of procedure memory, processes often relies on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}. Therefore, they also fail to achieve high NTIC as well.

             This is similar to the model-free policy-based agents in the reinforcement learning framework. The process of a system only maps the input state space to the action state space \needref{11}. The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
            % @ $\pi : S \times A$\\
            % Policy
    		\begin{equation}
    			\label{eq:PolicyBasedAgent}
    			\begin{aligned}
    			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
    			\end{aligned}
    		\end{equation}

    		This can explain why the patient D.F., who has apperceptive agnosia, can perform online motor controls without visual awareness of the action targets  \citep{10.3389/fneur.2014.00255}.
    		Our theory also explains why the unconscious processing in this category often fail when long delay periods are introduced in the tasks. Because without self-predicitve information in NTIC, the policies of motor outputs largely depends on the present sensory states implying that this type of processes can only perform online. With certain delays, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.

    		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because there is no way to maintain any form of memory of a system and such that there is zero influence from the system past states to its future state. On the contrary, with recurrent loops, a neural network can create information channels from its past to its future and becomes capable of achieving NTIC. This result coincide with some theories of consciousness which hypothesise the recurrent neural circuits as the NCC \needref{recurrent and NCC}. However, we derive this conclusion from a more fundamental informational-related hypothesis showing that our theory has a stronger explanatory power. 
\rlend

        \subsubsection{Fail to meet 2\lowercase{ed} condition}

		\begin{figure}[H]
			\includegraphics[width=1.3\textwidth]{WritingMaterials/Fig_Temperature_Example/ExampleOfCG.pdf}
			\centering
			\caption{An Example of ...}
			\label{fig:TemperatureExample}
		\end{figure}   
\rlstart{3}        
            \begin{ants}
                @ Due to the coarse-grained level-dependence of information processing, if a process is not at levels achieving NTIC, the information remains unconscious.

        	    @ Even though a system can form NTIC processes at some certain coarse-grained levels, information processing outside these levels remains unconscious.

        	    @ The first implication from this scenario is that processes at levels with high stochasticity are unable to achieve high NTIC and hence unconscious. High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process.

        	    @ In the neural system, the cellular level activities are highly noisy.

        	    @ This prevents information from cellular activities from forming high NTIC processes.

        	    @ Therefore, we never can be aware of detail activities at microscopic in the neural system.

        	    @ Some may argue that empirical evidence suggests single cell level correlation of conscious experience, the Jennifer Aniston cell for example.

        	    @ However, to note that, the correlation is always not the microscopic state changes of the cells, e.g. the action potentials. Instead, the correlated variables are always coarse-grained, for example the firing rate which is temporal coarse-grained variables.

        	    @ Second, it has been well established that heterogeneous nonlinearity is crucial for neural populations to encode rich and high dimensional information. \citep{Chelaru2008, Rigotti2010Oct, Shamir2004Jun}. Finding a single neuron whose activities align with a subspace representing a single object within the state space of a population code. \ideaCallout{Not sure if I want to add this point}

        	    @ This also explains why we are not aware of probabilistic inference performed by the neural system but only a "sample" of W

        	    @ Previous studies have showed that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way.

        	    @ However, we are ignorant nearly all the computation when the neural system performs probabilistic inference.

        	    @ Fig. \ref{fig:TemperatureExample} showed that because the computation is performed at microscopic levels, only the macroscopic variables, e.g. the summary statistics, are at the level with NTIC and become conscious.

        	    % Libet's experient

        	    @ The same scenario can also explain the results of Libet's experiment. In this experiment, in this experiment, Libet found that the neural activities (indicated by event-related potential) start earlier than the feeling of intention to perform an self-determined action.

        	    @ \citeauthor{schurger2012accumulat}

        	    @ The movement preparation initiates at the microscopic level.

        	    @ However, coarse-graining always maps a larger state space at microscopic levels to a equal or smaller state space at macroscopic levels (i.e. a surjective function). As the result, the state transitions at microscopic levels do not always lead to state transitions at macroscopic levels.

        	    @ Therefore, the initiative neural correlates of the free motor actions remained unconscious until the macroscopic state transition at the NTIC level.

        	    % multistable perception
        	    In the case of multistable perception, at every moment, only a single macroscopic state is mapped from the microscopic levels, we can only be aware of one interpretation at every moment.

@@

        	   @  === boundary conditions  ===
        	   @ The third category is the boundary conditions.

@@

                @ \rewrite{Such unconscious systems compute with probability distributions, but only a single sample, drawn from this probabilistic distribution, becomes conscious at a given time ( 27 , 28 ). We may become aware of several alternative interpretations, but only by sampling their unconscious distributions over time ( 29 , 30 ).}

\rlends

		\subsection{Conscious Processing}

		To achieve high NTIC has evolutionary advantage. When a process achieves NTIC, the current state of the process contains the information about its future state (Eq. (5)). Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process. Cognitive functions recruiting forward models built upon it are conscious. (E.g., planning and imagination)

		It is important to note that we do suggest any functionalism of consciousness. Rather, we believe that information is fundamentally linked to consciousness. The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution \cite{Seth2009Encyclopediaofconsciousness}.

		\begin{ants}
		    @ If both conditions are satisfied, information within the NTIC process becomes conscious. 
		    @ Our theory suggests that conscious processing should be linked to cognitive functions that require forward models and predictive information \critical{Need to list items vary carefully here.}

		    @ Previous research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.

@@

	    \begin{WritingMaterials}
	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness. This evidences an important fact that consciousness is not necessay to these functions.

@@

		\subsection{Unconscious Processing}
		When processes fail to satisfy either of the two conditions, they remain unconscious. First, when processes do not meet the first condition, i.e. the information processed not at the certain coarse-grained level, the information will not be included in conscious contents. For example, we are never conscious of neural spike activities at microscopic levels (e.g. single cell activities) because information passing among individual neurons are not at the certain coarse-grained level. \todo{Rewording}Libet's free will experiment can be also explained by our theory. The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.

		Second, when processes do not meet the second condition, i.e. processes which do not achieve high NTIC will remain unconscious. This can explain why many "policy-based" processes are not conscious.\todo{Need a better term/way here} Policy-based here features those processes taking sensory information as input and directly outputting actions. Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure. Neural processes are included in this category, e.g. reflexive neural circuit, blindsight, procedure memory.

		To summarise, our theory can well explain the various findings with parsimonious assumptions.

>>>>

\documentclass[utf8]{article}
\usepackage{import}
\usepackage{WritingToolsByAcer}

@@

    \newpage
    \section*{Not decided terminology}
        \begin{ants}
            @ information * in the NTIC process
            @ Full and short name of this theory
            @ core "?" (entity) for conscious content 
            @ our theory? framework? proposal? 
            @ system? process?
            @ variable? node? element? member?
            @ TODO:
                @@ Change coarse-graining function to "aggregation function"
        \end{ants}

@@

		% TODO: is figure needed?
		\idea{Do I need a figure?, Something like this one?}
		\begin{figure}[H]
			\includegraphicsTodo[width=\textwidth/2]{WritingMaterials/Fig_temp/PDFXCview_2018-06-11_13-37-34.png}
			\cite{pennartz2017consciousness}
			\caption{xxxx}
	   	\end{figure}

@@

				\begin{figure}
					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv.pdf}
					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
					\label{fig:SystemAndEnv}
				\end{figure}

@@

			\begin{figure}[H]
				\includegraphicsTodo[width=\textwidth]{WritingMaterials/Fig_temp/Palmer2015.png}
				\caption{Figure adapted from \cite{sederberg2018learning}}
				\label{fig:sederberg2018learning}
			\end{figure}

@@

		\begin{figure}
			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/Fig_temp/PDFXCview_2018-06-08_14-24-03.png}
			\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
			\label{fig:NCG}
		\end{figure}

@@

					@@ \rewrite{
						Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli. These features consist of spatial-temporal sequences of action potentials distributed across neurons and/or time.}

@@

% ============================================================================ %
%               A neural coarse graining theory of consciousness               %
% ============================================================================ %
	\section{A neural coarse graining theory of consciousness}

@@

				\begin{figure}[H]				
				\includegraphics[width=\textwidth]{WritingMaterials/Fig_temp/FoxitReader_2019-01-31_19-03-59.png}
				\label{fig:LevelOfConsciousness}
				\caption{Level of coarse-graining and level of consciousness. The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
				\end{figure}
		\end{ants}

@@

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
				\label{fig:hierarchy}
			\end{figure}

@@

% ============================================================================ %
%                    Conscious versus Unconscious Processing                   %
% ============================================================================ %
	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
	    In this section, we show how our theory can explain and predict whether a process is conscious or unconscious. Our theory is based on minimal assumptions. Nonetheless, it demonstrates a strong exploratory and predictive power about the relationship between information processing in the neural system and conscious experience.

		Our theory argues that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.

@@

        We especially highlight the second condition because it is critically related to many empirical research results even though it is only a necessary condition. As we will describe in the followings, this theory can well explain enormous previous findings in consciousness science and further make strong predictions for future research. In this section, we discuss how the two informational-based conditions link to conscious experience.

        % ---------------------------------------------------------------------------- %
        %                            Unconscious Processing                            %
        % ---------------------------------------------------------------------------- %
        \subsection{Unconscious Processing}

        \subsubsection*{Fail to meet the 1\lowercase{st} condition}
            If a process fails to fulfil either of the two conditions, information remains unconscious. We first consider the scenario that a process fails to satisfy the first condition, i.e. the process fails to achieve high degree of NTIC. In the neural system many processes fall into this category.

        	Considering the objectives of achieving NTIC (Eq. \ref{eq:nticObjective}), if a process is unable to maximise the mutual information between its past and future states ($I(Y_{t+1};Y_{t})$), it results in low NTIC. The failure to maximise the mutual information implies the past states of the process itself has little influence on its future states. In the meantime, if environmental information is able to flow into the process, the process can still produces functional outputs based on the current state of the environment accordingly. However, in this circumstance, the future state of the process is largely determined by the environmental states. That is, the process is not informational closed (${J_{t}(E \rightarrow Y )} \not\approx 0$, Fig.\ref{fig:reflexive}).

            % or minimise $I(Y_{t+1};Y_{t}|E_{t})$

@@

            In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs. For actions, this type of processes only produces "reflective-like" behaviours. Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls \citep{casali2013theoretically}\needref{More referene}. We argue that information carried by this type of processes is unconscious due to its failure of achieving high NTIC, i.e., the first condition.

            The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing. Blindsight patients are able to track objects, avoid obstacles, and make above chance-level judgements without having any conscious perception about visual stimuli. We believe that these behaviours can be guided by direct stimulus-response mappings ($S\rightarrow{}R$). However, the direct $S\rightarrow{}R$ mappings also lead to non-NTIC neural processes  and, therefore, are unconscious. Similarly, in the case of procedure memory, processes always rely on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}. The information flow from the environment to the system is crucial to guide the state transition of procedural memory. Therefore, information processing of procedural memory also fails to achieve high NTIC and remain unconscious.

             This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework. The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
        % @ $\pi : S \times A$\\
        % Policy
    		\begin{equation}
    			\label{eq:PolicyBasedAgent}
    			\begin{aligned}
    			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
    			\end{aligned}
    		\end{equation}

    		Our theory can explain why the patients with visual apperceptive agnosia (e.g., the famous case D.F.\cite{james2003ventral}) can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}. The online visual information can be used to perform functional actions without forming a NTIC process. Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks. Without self-predictive information in NTIC, the policies of motor outputs largely depends on the present environmental and sensory states implying that this type of processes often can only work online. With a long, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.

    		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because it is unable to maintain any form of memory so that there is no influence from the system past states to its future state. In contrast, with recurrent loops, a neural network is able to create information channels from its past to its future states and becomes capable of achieving NTIC. This result coincides with some theories of consciousness which emphasize the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
    		% if more references are needed, check Eklund_2012_RECURRENT PROCESSING AND THE CONSCIOUSNESS.pdf
    		However, we derive this conclusion from a more fundamental informational-related hypothesis indicating the more generalised principle behind it.

        % ---------------------------------------------------------------------------- %
        %                                Fail to meet 2                                %
        % ---------------------------------------------------------------------------- %

        \subsubsection*{Fail to meet the 2\lowercase{ed} condition}
        As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales. If processes at some levels of a system are able to achieve high NTIC and become conscious, information at other levels still remains unconscious. The first implication of this argument is that processes at levels with high stochasticity are unable to achieve high NTIC and, therefore, unconscious. High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process. In the neural system, the cellular level activities are highly noisy and are unable to reach high NTIC. Therefore, the information processed by the microscopic levels in the neural system are not conscious and we never can experience detail activities in the microscopic levels.

        We argue that many mysterious results in previous research of consciousness are originated from inappropriate biological and behavioural measurement scale. In the following, we list some examples.

        Unconscious processing in this category of

        @ Evidence suggests that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way\needref{bayesian brain}. However, an intriguing fact is that we are nearly ignorant of all the probabilistic computation of the inference processes but are only aware of "a sample" of the posterior distributions of the inferences \citep{dehaene2017consciousness, vul2009attention, asplund2014attentional, vul2008temporal, moreno2011bayesian}. The information of all alternative possible states is unable to enter conscious contents. In short, one needs to explain why the neural system can hold the joint probability distributions of inferred variables but, however, only a realisation of the inference outcome becomes conscious. Based on our theory, we argue that the computation of statistical inference is carried out at microscopic levels of the neural system and the NTIC process correlated with conscious contents only possesses the coarse-grained information of the computation. The mapping from the microscopic to macroscopic states naturally leads to a single and stable state at the macroscopic levels.

        For example, Fig. \ref{fig:TemperatureExample} illustrates the relationship 
        At the left panel, two cups contain water with different volumes $V_t$ and temperatures $T_t$. Even though we know volumes and temperatures are coarse-grained macroscopic variables, the states of mixed water ($V_{t+1}$, $T_{t+1}$) can still be predicted without knowing any information from the microscopic levels (the molecular level),i.e., the information closure at the macroscopic level. Similarly, taking Bayesian inference as an example, the microscopic neuron populations are able to represent probabilistic distributions about inferred target variables and the neural networks perform the statistical inference to obtain the posterior distributions. However, enormous microscopic neural states can be coarse-grained into the same state of summary statistics (e.g., the mean $\mu_{t}$  and standard deviation $\sigma_{t}$) at a macroscopic level. The state transition ($\mu_{t+1}$ and $\sigma_{t}$) is also predictable without any additional information from microscopic levels. Therefore, consciousness can only "observe" the coarse-grained states without the knowledge of how the statistical inference is implemented and performed at the microscopic levels.

		\begin{figure}[H]
			\includegraphics[width=1.3\textwidth]{WritingMaterials/Fig_Temperature_Example/ExampleOfCG.pdf}
			\centering
			\caption{An Example of ...}
			\label{fig:TemperatureExample}
		\end{figure}

        The same scenario can be applied to the results from Libet's volition experimental paradigm \citep{Libet1983TimeOC, Libet1985Dec}. Experiments using similar procedures usually show that the recorded neural activities start earlier than subjects' feeling of their own intention to act in the self-determined experimental settings. We argue that free actions are initiated at the microscopic levels, for example, the random fluctuation in the neural system \citep{schurger_accumulator_2012}. However, the feeling of volition is information at the macroscopic level with NTIC. Due to the information closure, there is no way for the NTIC process to observe the information of the microscopic states, i.e. the initiation of actions.

        \idea{Not sure if I want to address this point}  Note that, some evidence suggests single-cell-level correlation of conscious experience, the Jennifer Aniston cell for example \citep{Quiroga2005Jun, Quiroga2012Jul}. This may seem to counter our argument that single-cell level information is incapable to be conscious. However, first, the correlations are always not the direct microscopic state changes of the cells, e.g. the action potentials. Instead, the correlated variables are always coarse-grained. The neuronal firing rate, for example, is a temporal coarse-grained variable. Second, it has been well established that heterogeneous nonlinearity is critical for neural populations to encode rich and high dimensional information. \citep{Chelaru2008, Rigotti2010Oct, Shamir2004Jun}. It is common to detecting a single neuron whose activity profile well align with a subspace which represents a single object within the state space of a population code.\needhelp{Maybe need to rewording here} We believe that multi-scale data and analyses are needed to elucidate whether single neuron behaviours are sufficiently representative for any type of conscious experience.

		\begin{ants}
        	@ \idea{Should I write the following points? Is this too much?}
        	@  === boundary conditions  === 
        	% multistable perception
        	    @ In the case of multistable perception, at every moment, only a single macroscopic state is mapped from the microscopic levels, we can only be aware of one interpretation at every moment.

@@

        	   @ The third category is the boundary conditions.

@@

		\subsection{Conscious Processing}
		When the both conditions are fulfilled, our theory suggests that the states of a NTIC process correspond to particular conscious contents and the information incorporated in the NTIC process is conscious. Due to the predictive nature about the environment dynamics of NTIC processes, to achieve high NTIC and to construct functions within the process have a huge evolutionary advantage. It is important to emphasise that our theory does not suggest any functionalism of consciousness. Rather, we argue that information fundamentally associates with consciousness. Nevertheless, consciousness research still suggests a strong functional relation between consciousness and some specific types of cognition and behaviours \citep{Seth2009Encyclopediaofconsciousness}. We believe that this relation comes from several special properties of NTIC and these properties support the foundations of many cognitive functions in the neural system.

		First, a NTIC process encodes predictive information about environmental dynamics. This is crucial for constructing forward models for predicting future states of the environment. Therefore, cognitive functions which require agent-scale prediction are likely to be accompanied by conscious experience. This properties is required by planning and also achieving long term goals.\needref{}

		Second, a NTIC process can be considered as a close form simulation machine. With a given initial state, the process can self-evolve and follow a certain trajectory in the state space. This trajectory can be seem as a simulation about the environmental transition. Therefore, a NTIC process can serve cognitive functions as a perfect simulation engine \citep{BERTSCHINGER.2006}. Accordingly, mental simulation, imagination, computing alternative realities, and generating counterfactual outcomes can be implemented with a NTIC process. \needref{}

	    Third, an important properties of NTIC processes is its high stability. The state transitions and trajectory are highly predictable. In such case, NTIC processes are more suitable for integrating information across larger time scales (above millisecond). Therefore, tasks which require to integrate information across time above the millisecond scale are often associated with conscious experience.

	    Fourth, a NTIC process as a closed system can still provide predictive information without new information flowing into the process. This is crucial for many types of off-line processing.

	    Fifth, any state of a NTIC process can be seem as a integration of multiple sources of information. For the human scale activities, to know certain transition about the environment, the NTIC process must include a high dimensional information from multiple modalities and have the knowledge about how the high dimensional data interact to each other. Without the knowledge and information, a process may not be capable of produce a stable state transitions which mimic the environmental dynamics. Thus, cognitive functions requiring this large scale integration are likely to be conscious. Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.

	    In sum, we argue that having a NTIC process is critical for survival in the evolution. It is likely that biological creatures acquired NTIC process at some stages in the evolution. And due to the fundamental relationship between information and consciousness, these biological agents also acquired different degrees of consciousness depending on the physical scales and the complexity of the environments they live in. Our theory well explains why some processes and functions in the neural system are conscious and some are not with only two parsimonious conditions.

		\begin{WritingMaterials}
		    @ Previous research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.

@@

            @ =============================================================================

	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness. This evidences an important fact that consciousness is not necessay to these functions.

@@

% ============================================================================ %
%                        Comparison with other theories                        %
% ============================================================================ %
	\section{Comparison with other theories}
	In this section, we compare our theory with other popular modern theories of consciousness. 1

		\subsection{Theories about multilevel views on consciousness and cognition}
		Previously, similar to our theory, several multilevel views on consciousness and cognition have been proposed. We shortly discuss two theories relevant to our current proposal.
            \subsubsection*{Level of Organisation \cite{wimsatt1994ontology}}
                As mentioned previously, the level of coarse-graining is different from the anatomical level.
                Pennartz focus more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}). Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}. However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy. 
                \ideaBox{Should I also deal with Marr's level of abstraction?}
